---
title: "PrOTYPE: Predictor of high-grade serous ovarian carcinoma molecular subtype  \nResearch Report"
output: word_document
params:
  qc_data: NA
  pred_data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r load}
qc_data <- params$qc_data
pred_data <- params$pred_data
has_spot <- any(grepl("SPOT", names(pred_data)))
```

# Clinical Details

Confirmed high-grade serous ovarian cancer.

```{r clinical-details}
clin <- data.frame(
  c("Sample ID:", "Gene RLF:", "Date Extracted:", "Specimen:", "Quality Control:"),
  c(qc_data[["sample"]], qc_data[["geneRLF"]], qc_data[["nanostring.date"]], "Ovarian tumour",
    as.character(qc_data[["QCFlag"]]))
)
pander::pander(clin, col.names = NULL, justify = "left")
```

# Method

RNA was extracted from high-grade serous ovarian tumour tissue and PrOTYPE, a model using a 60-gene NanoString expression assay including 5 control genes, is used to generate a prediction of molecular subtype: C1.MES, C2.IMM, C4.DIF, or C5.PRO.

# Results

```{r primary-result}
pred <- c("C1/Mesenchymal", "C2/Immunoreactive", "C4/Differentiated", "C5/Proliferative")
prob <- purrr::map_chr(pred_data[c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")],
                       scales::percent)

entropy <- round(pred_data[["entropy"]], 2)
conf <- ifelse(entropy < 1, "good", "little")

result <- data.frame(
  `Molecular Subtype` = pred,
  Probability = prob,
  check.names = FALSE,
  stringsAsFactors = FALSE
)
bold_row <- match(pred_data[["pred"]], rownames(result))
pander::pander(result, emphasize.strong.rows = bold_row, row.names = FALSE)
```

Predictive Entropy: `r entropy`

# Prediction and Entropy

The PrOTYPE assay reports a probability that a sample belongs to one of four gene expression-based molecular subtypes. These probabilities sum to 100%. The subtype with the highest probability is noted in bold as the dominant subtype. Predictive entropy is reported on a scale from 0-2 where 0 indicates a perfect classification and 2 indicates a random-chance classification. Entropy can be affected by specimen quality, assay condition, and specimen biology.

```{r spot, eval=has_spot}
cli::cat_line("# SPOT")
cli::cat_line(paste("SPOT Prediction:", round(pred_data[["SPOT_pred"]], 3)))
cli::cat_line(paste("SPOT Quintile:", pred_data[["SPOT_quintile"]]))
```
