---
title: "PrOTYPE: Predictor of high-grade serous ovarian carcinoma molecular subtype  \nResearch Report"
output: word_document
params:
  qc_data: NA
  pred_data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r load}
qc_data <- params$qc_data
pred_data <- params$pred_data
```

# Clinical Details

Confirmed high-grade serous ovarian cancer.

```{r clinical-details}
clin <- data.frame(
  c("Sample ID:", "Gene RLF:", "Date Extracted:", "Specimen:"),
  c(qc_data[["sample"]], qc_data[["geneRLF"]], qc_data[["nanostring.date"]], "Ovarian tumour")
)
pander::pander(clin, col.names = NULL, justify = "left")
```

# Method

RNA was extracted from high-grade serous ovarian tumour tissue and a 60-gene Nanostring expression assay including 5 control genes and 55-genes for prediction of molecular subtype. Data was used to classify the sample into 4 distinct molecular subtypes: C1.MES, C2.IMM, C4.DIF, or C5.PRO.

# QC

`r qc_data[["QCFlag"]]` (refer to data output for specific metrics)

# Results

```{r primary-result}
pred <- c("C1/Mesenchymal", "C2/Immunoreactive", "C4/Differentiated", "C5/Proliferative")
prob <- purrr::map_chr(pred_data[c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")],
                       scales::percent)

entropy <- round(pred_data[["entropy"]], 2)
conf <- ifelse(entropy < 1, "good", "little")

result <- data.frame(
  `Molecular Subtype` = pred,
  Probability = prob,
  check.names = FALSE,
  stringsAsFactors = FALSE
)
bold_row <- match(pred_data[["pred"]], rownames(result))
pander::pander(result, emphasize.strong.rows = bold_row, row.names = FALSE)
```

Predictive Entropy: `r entropy`

# Prediction and Entropy

The PrOTYPE assay will report a prediction (sum to 100%) for each of four gene-expression based molecular subtypes. The subtype with the highest prediction is noted as the dominant subtype. No thresholds are given. Predictive entropy (Entropy) is noted on a scale from 0-2 where 0 would indicate a perfect classification and 2 would indicate random-chance. Entropy can be affected by specimen quality, assay condition, and specimen biology.
