---
title: "PrOTYPE: Predictor of high-grade serous ovarian carcinoma molecular subtype\nResearch Report"
output: word_document
params:
  qc_data: NA
  pred_data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis")
```

```{r load}
qc_data <- params$qc_data
pred_data <- params$pred_data
```

# Clinical Details

Personal history of high-grade serous ovarian cancer.

```{r clinical-details}
clin <- data.frame(
  c("Sample ID:", "Gene RLF:", "Date Extracted:", "Specimen:"),
  c(qc_data[["sample"]], qc_data[["geneRLF"]], qc_data[["nanostring.date"]], "Ovarian tumour")
)
pander::pander(clin, col.names = NULL, justify = "left")
```

# Specimen

Archival formalin-fixed ovarian tissue from primary surgery.

# Method

RNA was extracted from fixed ovarian tissue and was run on the NanoString gene expression platform. The 55-gene NanoString expression assay was used to classify high grade serous ovarian cancer samples into 4 distinct molecular subtypes, C1, C2, C4, or C5.

# Primary result

```{r primary-result}
pred <- c("C1/Mesenchymal", "C2/Immunoreactive", "C4/Differentiated", "C5/Proliferative")
conf <- purrr::map_chr(pred_data[c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")],
                       scales::percent)
result <- data.frame(
  `Molecular Subtype` = pred,
  Probability = conf,
  check.names = FALSE,
  stringsAsFactors = FALSE
)
bold_row <- match(pred_data[["pred"]], rownames(result))
pander::pander(result, emphasize.strong.rows = bold_row, row.names = FALSE)
```

Predictive Entropy: `r round(pred_data[["entropy"]], 2)`

# Interpretation

Gene expression analysis demonstrates a `r result[bold_row, "Molecular Subtype"]` subtype with `r result[bold_row, "Probability"]` confidence. Patients with >80% confidence for a predicted subtype are eligible for subtype-specific clinical trials (e.g. Targeting CI high grade serous ovarian cancer). Predictive entropy ranges from 0 (perfect prediction) to 2 (random chance).

# Reference range

```{r reference-range}
ref_range <- data.frame(
  c(">80%", "50-80%", "<50%"),
  c("High confidence", "Moderate confidence", "Low confidence")
)
pander::pander(ref_range, col.names = NULL)
```
