---
output:
  word_document:
    reference_docx: styles.docx
params:
  outputDir: outputDir
---

# D.3 Biological Characterization of the Subtypes

```{r setup_D03, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "asis"
)
```

```{r load_D03}
# Load packages, helpers, input data
suppressPackageStartupMessages({
  library(pander)
  library(survival)
  library(survminer)
  library(here)
})
source(here("pipeline/7-supplementary/utils.R"))

panderOptions("keep.trailing.zeros", TRUE)

all_pred <- readr::read_csv(here("data/nstring/predictions.csv"),
                            col_types = list("X1" = readr::col_skip()))
final_preds <- readr::read_csv(file.path(params$outputDir, "gene_selection/final_model/Final_Predictions.csv"),
                               col_types = list("X1" = readr::col_skip()))
b1 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch1_20170217_updated.csv"),
                      col_types = readr::cols())
b2 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch2_20170221.csv"),
                      col_types = readr::cols())
b3 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch3_20170307_updated_NCO.csv"),
                      col_types = readr::cols())
b4 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch4_20170512.csv"),
                      col_types = readr::cols())
as_dat <- readxl::read_excel(here("data/nstring/Predictions_Anatomical_10FEB2019.xlsx"))
nec_dat <- readxl::read_excel(here("data/nstring/FinalSubtype_AnalyticFile.xlsx"))
cd8_dat <- suppressWarnings(
  readxl::read_excel(here("data/nstring/OTTA DB_CD8_20180821 for Mike_HGS CCC END_edit_all.xlsx"))
)

fig_path <- file.path(params$outputDir, "supplementary/figures/D03")
```

```{r clin_combine}
# Remove ARL samples
all_pred <- all_pred %>% 
  dplyr::filter(!grepl("ARL", ottaID))

final_preds <- final_preds %>% 
  dplyr::filter(!grepl("ARL", ottaID))

b4 <- b4 %>% 
  dplyr::filter(is.na(ARL_block)) %>% 
  dplyr::select(-ARL_block)

# Check column names
stopifnot(identical(names(b1), names(b2)))
stopifnot(identical(names(b2), names(b3)))
stopifnot(identical(names(b3), names(b4)))

# Anatomical sites
as_dat <- as_dat %>%
  dplyr::select(ottaID, `Anatomical-Category`)

# Necrosis
nec_dat <- nec_dat %>% 
  dplyr::select(ottaID = ottaid, SampleRegionNecrosis2)

# CD8
cd8_dat <- cd8_dat %>% 
  dplyr::select(ottaID = `OTTA ID`, CD8_MAX)

# Combine batches
clin_d <- rbind(b1, b2, b3, b4) %>% 
  dplyr::rename(ottaID = `OTTA ID`) %>% 
  dplyr::inner_join(as_dat, by = "ottaID") %>% 
  dplyr::inner_join(nec_dat, by = "ottaID") %>% 
  dplyr::left_join(cd8_dat, by = "ottaID")

# Check otta IDs
stopifnot(identical(all_pred[["ottaID"]], clin_d[["ottaID"]]))
stopifnot(identical(final_preds[["ottaID"]], clin_d[["ottaID"]]))
```

```{r calculate-survival}
# Format survival data
# per data dictionary: "OTTA data dictionary_20160914_nanostring.xlsx"
# finalstatus     1=alive; 2=dead; 8=did not follow
# progression_assumed     0=no no evidence or documentation of progression, and patient is still alive; 
#                         1=yes site coded as 'yes'; 
#                         2=assumed yes no evidence or documentation of progression, but patient died; progression assumed; 
#                         9 = unknown no information on progression or vital status available
# causedeath      refer to item 12 in OCAC Clinical Data Capture Guidelines, 
#                   1 = Progression of Disease - known or presumed, 
#                   2 = Treatment related, 
#                   3 = Other, 
#                   7 = Not applicable (i.e. still alive), 
#                   9 = Unknown 
# Covariates: BRCA 1/2 mut, residual disease, age, stage, final subtype (-mut, -res)
# Censor at 10 years
CUTOFF.YEAR <- 10
clin_d <- clin_d %>%
  dplyr::mutate(
    anatomical_site = dplyr::case_when(
      `Anatomical-Category` == "UNK" ~ "presumed adnexal",
      TRUE ~ `Anatomical-Category`
    ) %>% 
      factor(levels = c("adnexal", "omentum", "peritoneal", "upper genital track",
                        "lower genital track", "presumed adnexal")),
    cellularity = factor(
      `Sample Region Cellularity`,
      levels = c("0-20", "21-40", "41-60", "61-80", "81-100")
    ), 
    necrosis = dplyr::case_when(
      SampleRegionNecrosis2 == "1" ~ "none",
      SampleRegionNecrosis2 == "2" ~ "<=20%",
      SampleRegionNecrosis2 == "3" ~ ">20%",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("none"),
    cd8 = dplyr::case_when(
      CD8_MAX == 0 ~ "none",
      CD8_MAX == 1 ~ "low",
      CD8_MAX == 2 ~ "med",
      CD8_MAX == 3 ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      factor(levels = c("none", "low", "med", "high")),
    race_v1 = dplyr::case_when(
      race == "1" ~ "white",
      hispanic == 2 ~ "hispanic",
      race %in% c("2", "3", "4", "5") ~ "other",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("white"),
    residual_disease = dplyr::case_when(
      resdx == "1" ~ "no residual",
      resdx %in% c("2", "3", "4", "5", "6", "8") ~ "any residual",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("no residual"),
    brca_v1 = dplyr::case_when(
      brca1_2 %in% c("4", "6", "WT") ~ "all wildtypes",
      brca1_2 %in% c("1", "BRCA 1") ~ "pathogenic BRCA1 mutation",
      brca1_2 == "2" ~ "pathogenic BRCA2 mutation",
      TRUE ~ NA_character_
    ) %>% 
      factor(),
    brca_v2 = dplyr::case_when(
      brca1_2 %in% c("4", "6", "WT") ~ "all wildtypes",
      brca1_2 %in% c("1", "BRCA 1", "2", "3", "BRCA 1 and BRCA 2") ~ "pathogenic BRCA1/BRCA2/NOS mutation",
      TRUE ~ NA_character_
    ) %>% 
      factor(),
    age_dx = dplyr::case_when(
      refage_revised == "." ~ NA_real_,
      TRUE ~ as.numeric(refage_revised)
    ),
    int_yrs = dplyr::case_when(
      timeint_revised %in% "." ~ NA_real_,
      TRUE ~ as.numeric(timeint_revised) / 365.25
    ),
    age_int = age_dx + int_yrs,
    stage = dplyr::case_when(
      stagenew == "1" ~ "low",
      stagenew == "2" ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("low"),
    os_yrs = dplyr::case_when(
      timelastfu %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(timelastfu) / 365.25
    ),
    os_sts = dplyr::case_when(
      finalstatus == 1 ~ "os.censored",
      finalstatus == 2 ~ "os.event",
      TRUE ~ NA_character_
    ),
    os_yrs10 = ifelse(os_yrs < CUTOFF.YEAR, os_yrs, CUTOFF.YEAR),
    os_sts10 = dplyr::case_when(
      finalstatus == 1 | os_yrs10 < os_yrs ~ "os.censored",
      TRUE ~ os_sts
    ),
    dss_yrs = os_yrs,
    dss_sts = dplyr::case_when(
      causedeath == 1 ~ "dss.event",
      causedeath == 9 ~ NA_character_,
      TRUE ~ "dss.censored"
    ),
    dss_yrs10 = os_yrs10,
    dss_sts10 = dplyr::case_when(
      causedeath != 9 & dss_yrs10 < dss_yrs ~ "dss.censored",
      TRUE ~ dss_sts
    ),
    pfs_yrs = dplyr::case_when(
      daystoprogression %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(daystoprogression) / 365.25
    ),
    pfs_sts = dplyr::case_when(
      progression_assumed_OCAC == 0 ~ "pfs.censored",
      progression_assumed_OCAC %in% c(1, 2) ~ "pfs.event",
      TRUE ~ NA_character_
    ),
    pfs_yrs10 = ifelse(pfs_yrs < CUTOFF.YEAR, pfs_yrs, CUTOFF.YEAR),
    pfs_sts10 = dplyr::case_when(
      progression_assumed_OCAC == 0 | pfs_yrs10 < pfs_yrs ~ "pfs.censored",
      TRUE ~ pfs_sts
    ),
    age_os_lfu = age_dx + os_yrs,
    age_dss_lfu = age_dx + dss_yrs,
    age_pfs_lfu = age_dx + pfs_yrs,
    age_os_lfu10 = age_dx + os_yrs10,
    age_dss_lfu10 = age_dx + dss_yrs10,
    age_pfs_lfu10 = age_dx + pfs_yrs10,
    os_int = ifelse(int_yrs > os_yrs, os_yrs, os_yrs - int_yrs),
    dss_int = ifelse(int_yrs > os_yrs, dss_yrs, dss_yrs - int_yrs),
    pfs_int = ifelse(int_yrs > os_yrs, pfs_yrs, pfs_yrs - int_yrs),
    os_int10 = ifelse(int_yrs > os_yrs10, os_yrs10, os_yrs10 - int_yrs),
    dss_int10 = ifelse(int_yrs > os_yrs10, dss_yrs10, dss_yrs10 - int_yrs),
    pfs_int10 = ifelse(int_yrs > os_yrs10, pfs_yrs10, pfs_yrs10 - int_yrs)
  ) %>% 
  dplyr::mutate_at(dplyr::vars(dplyr::matches("sts")), as.factor)

# Join predictions with clinical data and modify case TVAN20158
d <-
  list(all_pred, final_preds, clin_d) %>%
  purrr::reduce(dplyr::inner_join, by = "ottaID") %>% 
  dplyr::mutate(
    final = factor(final),
    os_yrs = magrittr::inset(
      os_yrs,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    os_yrs10 = magrittr::inset(
      os_yrs10,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    dss_yrs = os_yrs,
    dss_yrs10 = os_yrs10,
    pfs_yrs = magrittr::inset(
      pfs_yrs,
      ottaID == "TVAN20158",
      NA_real_
    ),
    pfs_yrs10 = magrittr::inset(
      pfs_yrs10,
      ottaID == "TVAN20158",
      NA_real_
    )
  ) %>% 
  dplyr::rename(array_preds = Adaboost.xpn,
                TCGA_preds = TCGA.Predicted.Subtype) %>% 
  dplyr::mutate_at(c("array_preds", "TCGA_preds"), make.names)

# Concordant and Discordant samples
conc <- d %>% dplyr::filter(array_preds == TCGA_preds)
disc <- d %>% dplyr::filter(array_preds != TCGA_preds)

# make sure there are no os_yrs > 100 years
stopifnot(sum(d[["os_yrs"]] > 100, na.rm = TRUE) == 0)
```

## D.3.1 Correlation with Clinical and Pathological Parameters

### _Table SD8._ Molecular subtype by pathogenic BRCA mutation.

```{r subtype_by_brca}
sb_tab <- dplyr::inner_join(
  Amisc::describeBy(d, "final", by1 = "brca_v1", digits = 1),
  Amisc::describeBy(d, "final", by1 = "brca_v2", digits = 1),
  by = c("Levels", "all wildtypes")
) %>% 
  dplyr::select(2:5, 9) %>% 
  dplyr::slice(-1)
pandoc.table(sb_tab, split.tables = Inf)
```

### Boxplot of Year of Diagnosis by Subtype

```{r year_dx_by_subtype, fig.width=7, fig.height=5}
bp_dat <- d %>%
  dplyr::filter(anatomical_site %in% c("adnexal", "presumed adnexal")) %>% 
  dplyr::transmute(
    dxyear = as.numeric(refage_revised) + as.numeric(dobyear),
    final
  )

num5 <- fivenum(bp_dat[["dxyear"]])
iqr <- paste(num5[c(2, 4)], collapse = " - ")
num5_text <- paste0(c("Min", "Median (IQR)", "Max"),
                    ": ",
                    c(num5[1], paste0(num5[3], " (", iqr, ")"), num5[5]),
                    collapse = ", ")

p <- ggplot(bp_dat, aes(final, dxyear)) +
  geom_boxplot(varwidth = TRUE, outlier.shape = NA, coef = 0,
               fill = "#D1D1D1", color = "white", na.rm = TRUE) +
  geom_dotplot(method = "histodot", binwidth = 1, binaxis = "y", dotsize = 0.05,
               color = "#3A6EE3", na.rm = TRUE) +
  labs(
    x = "Final Subtype",
    y = "Year of Diagnosis",
    title = "Year of Diagnosis by HGSC Final Subtype Classification",
    subtitle = paste0("All Adnexal and Presumed Adnexal n=", nrow(bp_dat), ", ", num5_text)
  ) +
  theme_minimal() +
  theme(panel.grid.major.x = element_blank(),
        plot.subtitle = element_text(size = 10))

# print(p)
ggsave(file.path(fig_path, "year_dx_by_subtype.pdf"), p, width = 7, height = 5)
```

### _Table SD9:_ Cohort characteristics for known and presumed adnexal sites by subtype

```{r cohort_characteristics_all}
var_names <- c("age_dx", "stage", "residual_disease", "cellularity",
               "necrosis", "brca_v1", "race_v1", "cd8", "anatomical_site")
var_desc <- c("Age at Diagnosis", "Stage", "Residual Disease", "Cellularity",
              "Necrosis", "BRCA1/BRCA2", "Race", "CD8", "Anatomical Site")
d_cohort_adnexal_all <- d %>%
  dplyr::transmute(final, !!!rlang::syms(var_names)) %>% 
  dplyr::filter(anatomical_site %in% c("adnexal", "presumed adnexal"))
uni_ass_adnexal_all <- d_cohort_adnexal_all %>% 
  Amisc::describeBy(var_names, var_desc, "final", dispersion = "sd", digits = 1, p.digits = 4)
pandoc.table(uni_ass_adnexal_all, split.tables = Inf,
             caption = "Cohort characteristics for all cases by subtype")
```

### _Table SD10:_ Cohort characteristics for known adnexal sites by subtype

```{r cohort_characteristics_adnexal}
d_cohort_adnexal_only <- d_cohort_adnexal_all %>% 
  dplyr::filter(anatomical_site == "adnexal")
var_names_adnexal_only <- var_names %>% purrr::discard(~ . == "anatomical_site")
var_desc_adnexal_only <- var_desc %>% purrr::discard(~ . == "Anatomical Site")
uni_ass_adnexal_only <- d_cohort_adnexal_only %>% 
  Amisc::describeBy(var_names_adnexal_only, var_desc_adnexal_only, "final", dispersion = "sd", digits = 1, p.digits = 4)
pandoc.table(uni_ass_adnexal_only, split.tables = Inf,
             caption = "Cohort characteristics for all known ovarian site by subtype")
```

### _Table SD11:_ Median Follow-up Time in Years and Events by Final Subtype

```{r follow_up}
# Calculate follow-up times summarized with the median
fu_times <- function(data, time, status, event, group = NULL, digits = 1) {
  if (!is.null(group)) {
    data <- dplyr::group_by(data, .data[[group]])
  }
  fu_dat <- data %>% 
    dplyr::summarize(
      `Observation Time` = median(.data[[time]], na.rm = TRUE),
      `Censoring Time` = median(.data[[time]][.data[[status]] == event], na.rm = TRUE),
      `Reverse KM` = survfit(Surv(.data[[time]], ifelse(.data[[status]] == event, 0, 1)) ~ 1) %>% 
        broom::glance() %>% 
        purrr::pluck("median"),
      Events = sum(.data[[status]] == event, na.rm = TRUE)
    ) %>% 
    dplyr::mutate_if(is.numeric, round, digits = digits)
  if (!is.null(group)) {
    dplyr::rename(fu_dat, Class = group)
  } else {
    tibble::add_column(fu_dat, Class = "Full Cohort", .before = 1)
  }
}
```

```{r times_total}
os_args <- list(time = "os_int", status = "os_sts", event = "os.event")
pfs_args <- list(time = "pfs_int", status = "pfs_sts", event = "pfs.event")

os_full <- purrr::invoke(fu_times, os_args, data = d)
pfs_full <- purrr::invoke(fu_times, pfs_args, data = d)

os_conc <- purrr::invoke(fu_times, os_args, data = conc)
pfs_conc <- purrr::invoke(fu_times, pfs_args, data = conc)
```

```{r times_final_os}
times_final_os <- os_full %>% 
  rbind(purrr::invoke(fu_times, os_args, data = d, group = "final"))
pandoc.table(
  times_final_os,
  caption = "OS Median Follow-up Time in Years by Final Predictions"
)
```

\  

```{r times_final_pfs}
times_final_pfs <- pfs_full %>% 
  rbind(purrr::invoke(fu_times, pfs_args, data = d, group = "final"))
pandoc.table(
  times_final_pfs,
  caption = "PFS Median Follow-up Time in Years by Final Predictions"
)
```

## D.3.3 Survival Analysis

```{r surv_params_C03}
# Common km arguments (Display legend only for top (OS) survival plot)
km_args <- list(ylab = c("Overall survival", "Progression-free survival"),
                legend = c(list(c(0.9, 0.9)), "none"))

# Common survival plot arguments
surv_args <- list(
  data = d,
  conf.int = TRUE,
  pval = TRUE,
  pval.method = TRUE,
  pval.coord = c(0, 0.1),
  pval.method.coord = c(0, 0.20),
  risk.table = TRUE,
  risk.table.height = 1/3,
  xlab = "Time in Years",
  legend.title = "Subtype",
  legend.labs = c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")
)

# Common combine plot arguments
comb_args <- list(print = FALSE, ncol = 1, nrow = 2)
```

```{r km_final_aa, fig.width=7, fig.height=10}
# Filter for all adnexal sites
d_aa <- dplyr::filter(d, anatomical_site %in% c("adnexal", "presumed adnexal"))
surv_args_aa <- purrr::map_at(surv_args, "data", ~ d_aa)

km_final_aa <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_int10, os_sts10 == "os.event") ~ final, data = d_aa),
    survfit(Surv(pfs_int10, pfs_sts10 == "pfs.event") ~ final, data = d_aa)
  )
)
plots_km_final_aa <- km_final_aa %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args_aa, ylab = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "Adnexal and Presumed Adnexal Sites OTTA (Final Model)")
ggsave(file.path(fig_path, "km_final_adnexal_all.pdf"), plots_km_final_aa, width = 7, height = 10)
```

```{r km_final_ka, fig.width=7, fig.height=10}
# Filter for known adnexal sites
d_ka <- dplyr::filter(d, anatomical_site == "adnexal")
surv_args_ka <- purrr::map_at(surv_args, "data", ~ d_ka)

km_final_ka <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_int10, os_sts10 == "os.event") ~ final, data = d_ka),
    survfit(Surv(pfs_int10, pfs_sts10 == "pfs.event") ~ final, data = d_ka)
  )
)
plots_km_final_ka <- km_final_ka %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args_ka, ylab = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "Adnexal Sites OTTA (Final Model)")
ggsave(file.path(fig_path, "km_final_adnexal_known.pdf"), plots_km_final_ka, width = 7, height = 10)
```

```{r rm_rplots_D03}
file.remove(here::here("Rplots.pdf"))
```

```{r mvs_dat}
# Covariate variable arguments
var_all <- purrr::set_names(
  c("final", "age_dx", "stage", "cd8", "residual_disease",  "brca_v1"),
  c("Final Subtype", "Age", "Stage", "CD8", "Residual Disease", "BRCA1/BRCA2")
)
var_lists <- tibble::lst(
  var_base = purrr::keep(var_all, ~ . %in% c("final", "age_dx", "stage")),
  var_add_cd8 = c(var_base, var_all["CD8"]),
  var_add_resdx = c(var_add_cd8, var_all["Residual Disease"]),
  var_add_brca = c(var_add_resdx, var_all["BRCA1/BRCA2"])
)
# Base title
title_base <- "Multivariable survival analysis of overall and progression-free survival, adjusting for"

# Multivariate survival data sources
mvs_dat <- d %>% 
  dplyr::transmute(
    final = forcats::fct_relevel(final, "C1.MES", after = Inf),
    residual_disease,
    brca_v1,
    age_dx,
    stage,
    anatomical_site,
    cd8,
    os_yrs,
    os_sts,
    pfs_yrs,
    pfs_sts,
    age_int,
    age_os_lfu,
    age_pfs_lfu
  ) %>% 
  as.data.frame()

# Filtered by anatomical site
mvs_dat_adnexal_all <- mvs_dat %>% 
  dplyr::filter(anatomical_site %in% c("adnexal", "presumed adnexal"))
mvs_dat_adnexal_only <- mvs_dat %>% 
  dplyr::filter(anatomical_site == "adnexal")

# Complete cases for each outcome
mvs_dat_adnexal_all_comp <- mvs_dat_adnexal_all %>% 
  tidyr::drop_na(var_all)
mvs_dat_adnexal_only_comp <- mvs_dat_adnexal_only %>% 
  tidyr::drop_na(var_all)

# Multivarite survival arguments
mvs_args <- list(
  stat.test = "logtest",
  var.names.surv.time = c("age_int", "age_int"),
  var.names.surv.time2 = c("age_os_lfu", "age_pfs_lfu"),
  var.names.surv.status = c("os_sts", "pfs_sts"),
  event.codes.surv = c("os.event", "pfs.event"),
  surv.descriptions = c("OS", "PFS"),
  show.var.detail = TRUE,
  show.group.name.for.bin.var = TRUE,
  round.small = TRUE,
  caption = NULL
)
```

### Known and Presumed Adnexal Sites

```{r mvs_all}
# Multivariable Survival for all adexnal sites
mvs_all <- purrr::invoke_map(
  .f = biostatUtil::doCoxphMultivariable,
  .x = var_lists %>% purrr::map(
    ~ purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.)
    )
  ),
  input.d = mvs_dat_adnexal_all
) %>% 
  purrr::set_names(names(var_lists))

# Titles for all adnexal sites
titles_all <- var_lists %>%
  purrr::map( ~ {
    paste(title_base,
          paste(names(.), collapse = ", "),
          "(known and presumed adnexal sites)")
  })
```

### `r titles_all[["var_base"]]`

```{r mvs_all_base}
cat(purrr::pluck(mvs_all, "var_base", "result.table.bamboo"))
```

### `r titles_all[["var_add_cd8"]]`

```{r mvs_all_add_cd8}
cat(purrr::pluck(mvs_all, "var_add_cd8", "result.table.bamboo"))
```

### `r titles_all[["var_add_resdx"]]`

```{r mvs_all_add_resdx}
cat(purrr::pluck(mvs_all, "var_add_resdx", "result.table.bamboo"))
```

### `r titles_all[["var_add_brca"]]`

```{r mvs_all_add_brca}
cat(purrr::pluck(mvs_all, "var_add_brca", "result.table.bamboo"))
```

### Known Adnexal Sites

```{r mvs_known}
# Multivariable Survival for known adexnal sites
mvs_known <- purrr::invoke_map(
  .f = biostatUtil::doCoxphMultivariable,
  .x = var_lists %>% purrr::map(
    ~ purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.)
    )
  ),
  input.d = mvs_dat_adnexal_only
) %>% 
  purrr::set_names(names(var_lists))

# Titles for known adnexal sites
titles_known <- var_lists %>%
  purrr::map( ~ {
    paste(title_base,
          paste(names(.), collapse = ", "),
          "(known adnexal sites)")
  })
```

### `r titles_known[["var_base"]]`

```{r mvs_known_base}
cat(purrr::pluck(mvs_known, "var_base", "result.table.bamboo"))
```

### `r titles_known[["var_add_cd8"]]`

```{r mvs_known_add_cd8}
cat(purrr::pluck(mvs_known, "var_add_cd8", "result.table.bamboo"))
```

### `r titles_known[["var_add_resdx"]]`

```{r mvs_known_add_resdx}
cat(purrr::pluck(mvs_known, "var_add_resdx", "result.table.bamboo"))
```

### `r titles_known[["var_add_brca"]]`

```{r mvs_known_add_brca}
cat(purrr::pluck(mvs_known, "var_add_brca", "result.table.bamboo"))
```

### Known and Presumed Adnexal Sites, Complete Cases

```{r mvs_all_comp}
# Multivariable Survival for all adexnal sites
mvs_all_comp <- purrr::invoke_map(
  .f = biostatUtil::doCoxphMultivariable,
  .x = var_lists %>% purrr::map(
    ~ purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.)
    )
  ),
  input.d = mvs_dat_adnexal_all_comp
) %>% 
  purrr::set_names(names(var_lists))

# Titles for all adnexal sites, complete cases
titles_all_comp <- var_lists %>%
  purrr::map( ~ {
    paste(title_base,
          paste(names(.), collapse = ", "),
          "(known and presumed adnexal sites, complete cases)")
  })
```

### `r titles_all_comp[["var_base"]]`

```{r mvs_all_comp_base}
cat(purrr::pluck(mvs_all_comp, "var_base", "result.table.bamboo"))
```

### `r titles_all_comp[["var_add_cd8"]]`

```{r mvs_all_comp_add_cd8}
cat(purrr::pluck(mvs_all_comp, "var_add_cd8", "result.table.bamboo"))
```

### `r titles_all_comp[["var_add_resdx"]]`

```{r mvs_all_comp_add_resdx}
cat(purrr::pluck(mvs_all_comp, "var_add_resdx", "result.table.bamboo"))
```

### `r titles_all_comp[["var_add_brca"]]`

```{r mvs_all_comp_add_brca}
cat(purrr::pluck(mvs_all_comp, "var_add_brca", "result.table.bamboo"))
```

### Known Adnexal Sites, Complete Cases

```{r mvs_known_comp}
# Multivariable Survival for all adexnal sites
mvs_known_comp <- purrr::invoke_map(
  .f = biostatUtil::doCoxphMultivariable,
  .x = var_lists %>% purrr::map(
    ~ purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.)
    )
  ),
  input.d = mvs_dat_adnexal_only_comp
) %>% 
  purrr::set_names(names(var_lists))

# Titles for known adnexal sites, complete cases
titles_known_comp <- var_lists %>%
  purrr::map( ~ {
    paste(title_base,
          paste(names(.), collapse = ", "),
          "(known adnexal sites, complete cases)")
  })
```

### `r titles_known_comp[["var_base"]]`

```{r mvs_known_comp_base}
cat(purrr::pluck(mvs_known_comp, "var_base", "result.table.bamboo"))
```

### `r titles_known_comp[["var_add_cd8"]]`

```{r mvs_known_comp_add_cd8}
cat(purrr::pluck(mvs_known_comp, "var_add_cd8", "result.table.bamboo"))
```

### `r titles_known_comp[["var_add_resdx"]]`

```{r mvs_known_comp_add_resdx}
cat(purrr::pluck(mvs_known_comp, "var_add_resdx", "result.table.bamboo"))
```

### `r titles_known_comp[["var_add_brca"]]`

```{r mvs_known_comp_add_brca}
cat(purrr::pluck(mvs_known_comp, "var_add_brca", "result.table.bamboo"))
```
