---
output:
  word_document:
    reference_docx: styles.docx
params:
  outputDir: outputDir
---

# B.7 Subtype Assignment in the NanoString Data

```{r setup_B07, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "asis"
)
```

```{r load_B07}
# Load packages, helpers, input data
library(pander)
library(survival)
library(survminer)
library(ggplot2)
library(here)
source(here("pipeline/7-supplementary/utils.R"))

panderOptions("keep.trailing.zeros", FALSE)
panderOptions("table.split.table", Inf)
n_genes <- 55
grm <- "CTHRC1"

raw_ns <- load_nanostring()
arl_samples <- readxl::read_excel(here("data/nstring/Nanostring_ARL-all samples-all gnes_20180607.xlsx"))
all_pred <- readr::read_csv(here("data/nstring/predictions.csv"),
                            col_types = list("X1" = readr::col_skip()))
sum_freq <- readr::read_csv(file.path(params$outputDir, "gene_selection/sum_freq/overall_freq.csv"),
                            col_types = readr::cols())
array_probs <- readr::read_csv(file.path(params$outputDir, "nanostring/predictions/aa_probs.csv"),
                               col_types = readr::cols())
tcga_probs <- readr::read_csv(file.path(params$outputDir, "nanostring/predictions/tcga_probs.csv"),
                              col_types = readr::cols())
final_preds <- readr::read_csv(file.path(params$outputDir, "gene_selection/final_model/Final_Predictions.csv"),
                               col_types = list("X1" = readr::col_skip()))
final_model <- readRDS(file.path(params$outputDir, "gene_selection/final_model/final_model.rds"))
b1 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch1_20170217_updated.csv"),
                      col_types = readr::cols())
b2 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch2_20170221.csv"),
                      col_types = readr::cols())
b3 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch3_20170307_updated_NCO.csv"),
                      col_types = readr::cols())
b4 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch4_20170512.csv"),
                      col_types = readr::cols())
as_dat <- readxl::read_excel(here("data/nstring/Predictions_Anatomical_18DEC2018MA.xlsx"))
nec_dat <- readxl::read_excel(here("data/nstring/FinalSubtype_AnalyticFile.xlsx"))
cd8_dat <- readxl::read_excel(here("data/nstring/OTTA DB_CD8_20180821 for Mike_HGS CCC END_edit_all.xlsx"))

fig_path <- file.path(params$outputDir, "supplementary/figures/B07")
```

## Agreement between All-Array and TCGA

```{r aa_tcga_table}
pred_tab <- all_pred %>% 
  dplyr::filter(!ottaID %in% arl_samples[["OTTA ID"]]) %>% 
  with(., table(
    `Predicted Array` = make.names(Adaboost.xpn),
    `Predicted TCGA` = make.names(TCGA.Predicted.Subtype)
  )) %>% 
  caret::confusionMatrix()
```

### A - Confusion Matrix

```{r aa_tcga_confmat}
pandoc.table(ftable(pred_tab[["table"]]))
```

### B - Overall Metrics

Cohen's Kappa measures inter-rater agreement while taking into account the expected values and agreement by random chance.

```{r aa_tcga_overall_metrics}
ov_metrics <- confmat_metrics(pred_tab, metrics = "overall")
pandoc.table(ov_metrics)
```

### C - By-Class Metrics

```{r aa_tcga_by-class_metrics}
bc_metrics <- confmat_metrics(pred_tab, metrics = "byclass")
pandoc.table(bc_metrics, keep.trailing.zeros = TRUE)
```

## Predictive Entropy

```{r entropy_compute}
# Merge probabilities and predictions
compare_probs <-
  dplyr::inner_join(array_probs,
                    tcga_probs,
                    by = "ottaID",
                    suffix = c("_array", "_tcga")) %>% 
  dplyr::inner_join(all_pred, by = "ottaID") %>%
  dplyr::filter(!ottaID %in% arl_samples[["OTTA ID"]]) %>% 
  dplyr::rename(predicted_array = Adaboost.xpn,
                predicted_tcga = TCGA.Predicted.Subtype) %>%
  dplyr::mutate_at(c("predicted_array", "predicted_tcga"), make.names)

# Compute entropies
entropy_probs <- compare_probs %>%
  dplyr::transmute(
    ottaID,
    entropy_array = apply(.[grep("(?<!predicted)_array", names(.), perl = TRUE)], 1,
                          entropy::entropy, unit = "log2"),
    entropy_tcga = apply(.[grep("(?<!predicted)_tcga", names(.), perl = TRUE)], 1,
                         entropy::entropy, unit = "log2"),
    predicted_array,
    predicted_tcga,
    match = factor(
      ifelse(predicted_array == predicted_tcga, "Consensus", "Non-Consensus"),
      levels = c("Consensus", "Non-Consensus")
    )
  ) %>%
  dplyr::mutate_at(dplyr::vars(dplyr::contains("entropy")), round, digits = 3)
```

### Mann-Whitney U Test

The null hypothesis tested within each data source is that a randomly sampled entropy score from samples with prediction agreement will be less than or greater than a randomly sampled entropy score with prediction disagreement with equal probability.

#### All-Array Entropies

```{r mwu_aa}
mwu_aa <- wilcox.test(entropy_array ~ match, entropy_probs) %>% broom::tidy()
pandoc.table(mwu_aa)
```

#### TCGA Entropies

```{r mwu_tcga}
mwu_tcga <- wilcox.test(entropy_tcga ~ match, entropy_probs) %>% broom::tidy()
pandoc.table(mwu_tcga)
```

### Entropy Plots on the entire NanoString data

#### Scatterplot Comparison

```{r scatterplot_args}
aa_vs_tcga_args <- list(
  scale_color_discrete(drop = FALSE),
  labs(x = "Adaboost - All Array",
       y = "Random Forest - TCGA"),
  theme_bw(),
  theme(legend.title = element_blank())
)
```

```{r entropy_scatterplot_agree, fig.height=5, fig.width=7}
p <- ggplot(entropy_probs, aes(entropy_array, entropy_tcga, color = match)) +
  geom_point(alpha = 0.5) +
  ggtitle("Entropy on full NanoString data by model agreement") +
  aa_vs_tcga_args

print(p)
ggsave(file.path(fig_path, "entropy_scatterplot_agree.pdf"), p, width = 7, height = 5)
```

```{r entropy_scatterplot_pred_aa, fig.height=5, fig.width=7}
p <- ggplot(entropy_probs, aes(entropy_array, entropy_tcga,
                               color = predicted_array)) +
  geom_point(alpha = 0.5) +
  ggtitle("Entropy on full NanoString data by predicted all array class") +
  aa_vs_tcga_args

print(p)
ggsave(file.path(fig_path, "entropy_scatterplot_pred_aa.pdf"), p, width = 7, height = 5)
```

```{r entropy_scatterplot_pred_tcga, fig.height=5, fig.width=7}
p <- ggplot(entropy_probs, aes(entropy_array, entropy_tcga,
                               color = predicted_tcga)) +
  geom_point(alpha = 0.5) +
  ggtitle("Entropy on full NanoString data by predicted TCGA class") +
  aa_vs_tcga_args

print(p)
ggsave(file.path(fig_path, "entropy_scatterplot_pred_tcga.pdf"), p, width = 7, height = 5)
```

#### Boxplot Comparison

```{r entropy_boxplot}
entropy_probs_grouped <- entropy_probs %>% 
  tidyr::gather(key = Data, value = Entropy, 2:3) %>% 
  tidyr::gather(key = Prediction, value = Subtype, 2:3) %>% 
  dplyr::mutate(Data = factor(
    dplyr::case_when(
      Data == "entropy_array" ~ "All Array",
      Data == "entropy_tcga" ~ "TCGA",
      TRUE ~ NA_character_
    ),
    levels = c("All Array", "TCGA")
  ))
```

```{r entropy_boxplot_agree, fig.height=5, fig.width=7}
p <- ggplot(entropy_probs_grouped, aes(Data, Entropy, fill = match)) +
  geom_boxplot() +
  ggtitle("Entropy Comparison of Prediction Labels by Data") +
  scale_fill_brewer(palette = "Set2") +
  theme_bw() +
  theme(legend.title = element_blank())

print(p)
ggsave(file.path(fig_path, "entropy_boxplot_agree.pdf"), p, width = 7, height = 5)
```

```{r entropy_boxplot_pred_aa, fig.height=5, fig.width=7}
p <- entropy_probs_grouped %>% 
  dplyr::filter(Data == "All Array") %>% 
  ggplot(aes(Subtype, Entropy, fill = match)) +
  geom_boxplot() +
  ggtitle("Entropy Comparison of All Array Prediction Labels by Subtype") +
  scale_fill_brewer(palette = "Set2") +
  theme_bw() +
  theme(legend.title = element_blank())

print(p)
ggsave(file.path(fig_path, "entropy_boxplot_pred_aa.pdf"), p, width = 7, height = 5)
```

```{r entropy_boxplot_pred_tcga, fig.height=5, fig.width=7}
p <- entropy_probs_grouped %>% 
  dplyr::filter(Data == "TCGA") %>% 
  ggplot(aes(Subtype, Entropy, fill = match)) +
  geom_boxplot() +
  ggtitle("Entropy Comparison of TCGA Prediction Labels by Subtype") +
  scale_fill_brewer(palette = "Set2") +
  theme_bw() +
  theme(legend.title = element_blank())

print(p)
ggsave(file.path(fig_path, "entropy_boxplot_pred_tcga.pdf"), p, width = 7, height = 5)
```

## Survival

```{r clin_combine_B07}
# Remove ARL samples
all_pred <- all_pred %>% 
  dplyr::filter(!grepl("ARL", ottaID))

final_preds <- final_preds %>% 
  dplyr::filter(!grepl("ARL", ottaID))

b4 <- b4 %>% 
  dplyr::filter(is.na(ARL_block)) %>% 
  dplyr::select(-ARL_block)

# Check column names
stopifnot(identical(names(b1), names(b2)))
stopifnot(identical(names(b2), names(b3)))
stopifnot(identical(names(b3), names(b4)))

# Anatomical sites
as_dat <- as_dat %>%
  dplyr::select(ottaID, `Anatomical-Category`)

# Necrosis
nec_dat <- nec_dat %>% 
  dplyr::select(ottaID = ottaid, SampleRegionNecrosis2)

# CD8
cd8_dat <- cd8_dat %>% 
  dplyr::select(ottaID = `OTTA ID`, CD8_MAX)

# Combine batches
clin_d <- rbind(b1, b2, b3, b4) %>% 
  dplyr::rename(ottaID = `OTTA ID`) %>% 
  dplyr::inner_join(as_dat, by = "ottaID") %>% 
  dplyr::inner_join(nec_dat, by = "ottaID") %>% 
  dplyr::left_join(cd8_dat, by = "ottaID")

# Check otta IDs
stopifnot(identical(all_pred[["ottaID"]], clin_d[["ottaID"]]))
stopifnot(identical(final_preds[["ottaID"]], clin_d[["ottaID"]]))
```

```{r calculate-survival_B07}
# Format survival data
# per data dictionary: "OTTA data dictionary_20160914_nanostring.xlsx"
# finalstatus     1=alive; 2=dead; 8=did not follow
# progression_assumed     0=no no evidence or documentation of progression, and patient is still alive; 
#                         1=yes site coded as 'yes'; 
#                         2=assumed yes no evidence or documentation of progression, but patient died; progression assumed; 
#                         9 = unknown no information on progression or vital status available
# causedeath      refer to item 12 in OCAC Clinical Data Capture Guidelines, 
#                   1 = Progression of Disease - known or presumed, 
#                   2 = Treatment related, 
#                   3 = Other, 
#                   7 = Not applicable (i.e. still alive), 
#                   9 = Unknown 
# Covariates: BRCA 1/2 mut, residual disease, age, stage, final subtype (-mut, -res)
# Censor at 10 years
CUTOFF.YEAR <- 10
clin_d <- clin_d %>%
  dplyr::mutate(
    anatomical_site = dplyr::case_when(
      `Anatomical-Category` == "UNK" ~ "presumed adnexal",
      TRUE ~ `Anatomical-Category`
    ) %>% 
      factor(levels = c("adnexal", "omentum", "peritoneal", "upper genital track",
                        "lower genital track", "presumed adnexal")),
    necrosis = dplyr::case_when(
      SampleRegionNecrosis2 == "1" ~ "none",
      SampleRegionNecrosis2 == "2" ~ "<=20%",
      SampleRegionNecrosis2 == "3" ~ ">20%",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("none"),
    cd8 = dplyr::case_when(
      CD8_MAX == 0 ~ "none",
      CD8_MAX == 1 ~ "low",
      CD8_MAX == 2 ~ "med",
      CD8_MAX == 3 ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      factor(levels = c("none", "low", "med", "high")),
    race_v1 = dplyr::case_when(
      race == "1" ~ "white",
      hispanic == 2 ~ "hispanic",
      race %in% c("2", "3", "4", "5") ~ "other",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("white"),
    residual_disease = dplyr::case_when(
      resdx == "1" ~ "no residual",
      resdx %in% c("2", "3", "4", "5", "6", "8") ~ "any residual",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("no residual"),
    BRCA1_2 = dplyr::case_when(
      brca1_2 %in% c("4", "6", "WT") ~ "all wildtypes",
      brca1_2 %in% c("1", "BRCA 1") ~ "pathogenic BRCA1 mutation",
      brca1_2 == "2" ~ "pathogenic BRCA2 mutation",
      brca1_2 %in% c("3", "BRCA 1 and BRCA 2") ~ "pathogenic NOS",
      TRUE ~ NA_character_
    ) %>% 
      factor(),
    age_dx = dplyr::case_when(
      refage_revised == "." ~ NA_real_,
      TRUE ~ as.numeric(refage_revised)
    ),
    stage = dplyr::case_when(
      stagenew == "1" ~ "low",
      stagenew == "2" ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("low"),
    os_yrs = dplyr::case_when(
      timelastfu %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(timelastfu) / 365.25
    ),
    os_sts = dplyr::case_when(
      finalstatus == 1 ~ "os.censored",
      finalstatus == 2 ~ "os.event",
      TRUE ~ NA_character_
    ),
    os_yrs10 = ifelse(os_yrs < CUTOFF.YEAR, os_yrs, CUTOFF.YEAR),
    os_sts10 = dplyr::case_when(
      finalstatus == 1 | os_yrs10 < os_yrs ~ "os.censored",
      TRUE ~ os_sts
    ),
    dss_yrs = os_yrs,
    dss_sts = dplyr::case_when(
      causedeath == 1 ~ "dss.event",
      causedeath == 9 ~ NA_character_,
      TRUE ~ "dss.censored"
    ),
    dss_yrs10 = os_yrs10,
    dss_sts10 = dplyr::case_when(
      causedeath != 9 & dss_yrs10 < dss_yrs ~ "dss.censored",
      TRUE ~ dss_sts
    ),
    pfs_yrs = dplyr::case_when(
      daystoprogression %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(daystoprogression) / 365.25
    ),
    pfs_sts = dplyr::case_when(
      progression_assumed_OCAC == 0 ~ "pfs.censored",
      progression_assumed_OCAC %in% c(1, 2) ~ "pfs.event",
      TRUE ~ NA_character_
    ),
    pfs_yrs10 = ifelse(pfs_yrs < CUTOFF.YEAR, pfs_yrs, CUTOFF.YEAR),
    pfs_sts10 = dplyr::case_when(
      progression_assumed_OCAC == 0 | pfs_yrs10 < pfs_yrs ~ "pfs.censored",
      TRUE ~ pfs_sts
    )
  ) %>% 
  dplyr::mutate_at(dplyr::vars(dplyr::matches("sts")), as.factor)

# Join predictions with clinical data and modify case TVAN20158
d <-
  list(all_pred, final_preds, clin_d) %>%
  purrr::reduce(dplyr::inner_join, by = "ottaID") %>% 
  dplyr::mutate(
    os_yrs = magrittr::inset(
      os_yrs,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    os_yrs10 = magrittr::inset(
      os_yrs10,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    dss_yrs = os_yrs,
    dss_yrs10 = os_yrs10,
    pfs_yrs = magrittr::inset(
      pfs_yrs,
      ottaID == "TVAN20158",
      NA_real_
    ),
    pfs_yrs10 = magrittr::inset(
      pfs_yrs10,
      ottaID == "TVAN20158",
      NA_real_
    )
  ) %>% 
  dplyr::rename(array_preds = Adaboost.xpn,
                TCGA_preds = TCGA.Predicted.Subtype) %>% 
  dplyr::mutate_at(c("array_preds", "TCGA_preds"), make.names)

# Concordant and Discordant samples
conc <- d %>% dplyr::filter(array_preds == TCGA_preds)
disc <- d %>% dplyr::filter(array_preds != TCGA_preds)

# make sure there are no os_yrs > 100 years
stopifnot(sum(d[["os_yrs"]] > 100, na.rm = TRUE) == 0)
```

```{r surv_params_B07}
# Common km arguments (Display legend only for top (OS) survival plot)
km_args <- list(title = c("Overall Survival", "Progression-Free Survival"),
                legend = c(list(c(0.9, 0.9)), "none"))

# Common survival plot arguments
surv_args <- list(
  data = d,
  conf.int = TRUE,
  pval = TRUE,
  pval.method = TRUE,
  risk.table = TRUE,
  risk.table.height = 1/3,
  xlab = "Time in Years",
  ylab = "Survival Probability",
  legend.title = "Class",
  legend.labs = c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")
)

# Common combine plot arguments
comb_args <- list(print = TRUE, ncol = 1, nrow = 2)
```

```{r km_all_array, fig.height=10, fig.width=7}
km_aa <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ array_preds, data = d),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ array_preds, data = d)
  )
)
plots_km_aa <- km_aa %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "All OTTA (All-Array Model)")
ggsave(file.path(fig_path, "km_all_array.pdf"), plots_km_aa, width = 7, height = 10)
```

```{r km_tcga, fig.height=10, fig.width=7}
km_tcga <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ TCGA_preds, data = d),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ TCGA_preds, data = d)
  )
)
plots_km_tcga <- km_tcga %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "All OTTA (TCGA Model)")
ggsave(file.path(fig_path, "km_tcga.pdf"), plots_km_tcga, width = 7, height = 10)
```

```{r km_conc, fig.height=10, fig.width=7}
km_conc <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ array_preds, data = conc),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ array_preds, data = conc)
  )
)
plots_km_conc <- km_conc %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "Concordant Samples")
ggsave(file.path(fig_path, "km_conc.pdf"), plots_km_conc, width = 7, height = 10)
```

```{r km_disc_all_array, fig.height=10, fig.width=7}
km_disc_aa <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ array_preds, data = disc),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ array_preds, data = disc)
  )
)
plots_km_disc_aa <- km_disc_aa %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "Discordant Samples (All-Array Model)")
ggsave(file.path(fig_path, "km_disc_all_array.pdf"), plots_km_disc_aa, width = 7, height = 10)
```

```{r km_disc_tcga, fig.height=10, fig.width=7}
km_disc_tcga <- purrr::list_merge(
  km_args,
  fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ TCGA_preds, data = disc),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ TCGA_preds, data = disc)
  )
)
plots_km_disc_tcga <- km_disc_tcga %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "Discordant Samples (TCGA Model)")
ggsave(file.path(fig_path, "km_disc_tcga.pdf"), plots_km_disc_tcga, width = 7, height = 10)
```
