---
output:
  word_document:
    reference_docx: styles.docx
params:
  outputDir: outputDir
---

# C.3 Biological Characterization of the Subtypes

```{r setup_C03, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "asis"
)
```

```{r load_C03}
# Load packages, helpers, input data
suppressPackageStartupMessages({
  library(pander)
  library(survival)
  library(survminer)
  library(biostatUtil)
  library(dplyr)
  library(magrittr)
  library(here)
})
source(here("pipeline/7-supplementary/utils.R"))

panderOptions("keep.trailing.zeros", TRUE)

all_pred <- readr::read_csv(here("data/nstring/predictions.csv"),
                            col_types = list("X1" = readr::col_skip()))
final_preds <- readr::read_csv(file.path(params$outputDir, "gene_selection/final_model/Final_Predictions.csv"),
                               col_types = list("X1" = readr::col_skip()))
b1 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch1_20170217_updated.csv"),
                      col_types = readr::cols())
b2 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch2_20170221.csv"),
                      col_types = readr::cols())
b3 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch3_20170307_updated_NCO.csv"),
                      col_types = readr::cols())
b4 <- readr::read_csv(here("data/nstring/nanostring_classifier_data_batch4_20170512.csv"),
                      col_types = readr::cols())
as_dat <- readxl::read_excel(here("data/nstring/Predictions_Anatomical_18DEC2018MA.xlsx"))
nec_dat <- readxl::read_excel(here("data/nstring/FinalSubtype_AnalyticFile.xlsx"))
cd8_dat <- suppressWarnings(
  readxl::read_excel(here("data/nstring/OTTA DB_CD8_20180821 for Mike_HGS CCC END_edit_all.xlsx"))
)
fig_path <- file.path(params$outputDir, "supplementary/figures/C03")
```

```{r clin_combine}
# Remove ARL samples
all_pred <- all_pred %>% 
  dplyr::filter(!grepl("ARL", ottaID))

final_preds <- final_preds %>% 
  dplyr::filter(!grepl("ARL", ottaID))

b4 <- b4 %>% 
  dplyr::filter(is.na(ARL_block)) %>% 
  dplyr::select(-ARL_block)

# Check column names
stopifnot(identical(names(b1), names(b2)))
stopifnot(identical(names(b2), names(b3)))
stopifnot(identical(names(b3), names(b4)))

# Anatomical sites
as_dat <- as_dat %>%
  dplyr::select(ottaID, `Anatomical-Category`)

# Necrosis
nec_dat <- nec_dat %>% 
  dplyr::select(ottaID = ottaid, SampleRegionNecrosis2)

# CD8
cd8_dat <- cd8_dat %>% 
  dplyr::select(ottaID = `OTTA ID`, CD8_MAX)

# Combine batches
clin_d <- rbind(b1, b2, b3, b4) %>% 
  dplyr::rename(ottaID = `OTTA ID`) %>% 
  dplyr::inner_join(as_dat, by = "ottaID") %>% 
  dplyr::inner_join(nec_dat, by = "ottaID") %>% 
  dplyr::left_join(cd8_dat, by = "ottaID")

# Check otta IDs
stopifnot(identical(all_pred[["ottaID"]], clin_d[["ottaID"]]))
stopifnot(identical(final_preds[["ottaID"]], clin_d[["ottaID"]]))
```

```{r calculate-survival}
# Format survival data
# per data dictionary: "OTTA data dictionary_20160914_nanostring.xlsx"
# finalstatus     1=alive; 2=dead; 8=did not follow
# progression_assumed     0=no no evidence or documentation of progression, and patient is still alive; 
#                         1=yes site coded as 'yes'; 
#                         2=assumed yes no evidence or documentation of progression, but patient died; progression assumed; 
#                         9 = unknown no information on progression or vital status available
# causedeath      refer to item 12 in OCAC Clinical Data Capture Guidelines, 
#                   1 = Progression of Disease - known or presumed, 
#                   2 = Treatment related, 
#                   3 = Other, 
#                   7 = Not applicable (i.e. still alive), 
#                   9 = Unknown 
# Covariates: BRCA 1/2 mut, residual disease, age, stage, final subtype (-mut, -res)
# Censor at 10 years
CUTOFF.YEAR <- 10
clin_d <- clin_d %>%
  dplyr::mutate(
    anatomical_site = dplyr::case_when(
      `Anatomical-Category` == "UNK" ~ "presumed adnexal",
      TRUE ~ `Anatomical-Category`
    ) %>% 
      factor(levels = c("adnexal", "omentum", "peritoneal", "upper genital track",
                        "lower genital track", "presumed adnexal")),
    necrosis = dplyr::case_when(
      SampleRegionNecrosis2 == "1" ~ "none",
      SampleRegionNecrosis2 == "2" ~ "<=20%",
      SampleRegionNecrosis2 == "3" ~ ">20%",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("none"),
    cd8 = dplyr::case_when(
      CD8_MAX == 0 ~ "none",
      CD8_MAX == 1 ~ "low",
      CD8_MAX == 2 ~ "med",
      CD8_MAX == 3 ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      factor(levels = c("none", "low", "med", "high")),
    race_v1 = dplyr::case_when(
      race == "1" ~ "white",
      hispanic == 2 ~ "hispanic",
      race %in% c("2", "3", "4", "5") ~ "other",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("white"),
    residual_disease = dplyr::case_when(
      resdx == "1" ~ "no residual",
      resdx %in% c("2", "3", "4", "5", "6", "8") ~ "any residual",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("no residual"),
    BRCA1_2 = dplyr::case_when(
      brca1_2 %in% c("4", "6", "WT") ~ "all wildtypes",
      brca1_2 %in% c("1", "BRCA 1") ~ "pathogenic BRCA1 mutation",
      brca1_2 == "2" ~ "pathogenic BRCA2 mutation",
      brca1_2 %in% c("3", "BRCA 1 and BRCA 2") ~ "pathogenic NOS",
      TRUE ~ NA_character_
    ) %>% 
      factor(),
    age_dx = dplyr::case_when(
      refage_revised == "." ~ NA_real_,
      TRUE ~ as.numeric(refage_revised)
    ),
    stage = dplyr::case_when(
      stagenew == "1" ~ "low",
      stagenew == "2" ~ "high",
      TRUE ~ NA_character_
    ) %>% 
      forcats::fct_relevel("low"),
    os_yrs = dplyr::case_when(
      timelastfu %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(timelastfu) / 365.25
    ),
    os_sts = dplyr::case_when(
      finalstatus == 1 ~ "os.censored",
      finalstatus == 2 ~ "os.event",
      TRUE ~ NA_character_
    ),
    os_yrs10 = ifelse(os_yrs < CUTOFF.YEAR, os_yrs, CUTOFF.YEAR),
    os_sts10 = dplyr::case_when(
      finalstatus == 1 | os_yrs10 < os_yrs ~ "os.censored",
      TRUE ~ os_sts
    ),
    dss_yrs = os_yrs,
    dss_sts = dplyr::case_when(
      causedeath == 1 ~ "dss.event",
      causedeath == 9 ~ NA_character_,
      TRUE ~ "dss.censored"
    ),
    dss_yrs10 = os_yrs10,
    dss_sts10 = dplyr::case_when(
      causedeath != 9 & dss_yrs10 < dss_yrs ~ "dss.censored",
      TRUE ~ dss_sts
    ),
    pfs_yrs = dplyr::case_when(
      daystoprogression %in% c("", ".") ~ NA_real_,
      TRUE ~ as.numeric(daystoprogression) / 365.25
    ),
    pfs_sts = dplyr::case_when(
      progression_assumed_OCAC == 0 ~ "pfs.censored",
      progression_assumed_OCAC %in% c(1, 2) ~ "pfs.event",
      TRUE ~ NA_character_
    ),
    pfs_yrs10 = ifelse(pfs_yrs < CUTOFF.YEAR, pfs_yrs, CUTOFF.YEAR),
    pfs_sts10 = dplyr::case_when(
      progression_assumed_OCAC == 0 | pfs_yrs10 < pfs_yrs ~ "pfs.censored",
      TRUE ~ pfs_sts
    )
  ) %>% 
  dplyr::mutate_at(dplyr::vars(dplyr::matches("sts")), as.factor)

# Join predictions with clinical data and modify case TVAN20158
d <-
  list(all_pred, final_preds, clin_d) %>%
  purrr::reduce(dplyr::inner_join, by = "ottaID") %>% 
  dplyr::mutate(
    os_yrs = magrittr::inset(
      os_yrs,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    os_yrs10 = magrittr::inset(
      os_yrs10,
      ottaID == "TVAN20158",
      difftime(as.Date("2007-10-27"), as.Date("2003-04-24"), units = "days") /
        365.241
    ),
    dss_yrs = os_yrs,
    dss_yrs10 = os_yrs10,
    pfs_yrs = magrittr::inset(
      pfs_yrs,
      ottaID == "TVAN20158",
      NA_real_
    ),
    pfs_yrs10 = magrittr::inset(
      pfs_yrs10,
      ottaID == "TVAN20158",
      NA_real_
    )
  ) %>% 
  dplyr::rename(array_preds = Adaboost.xpn,
                TCGA_preds = TCGA.Predicted.Subtype) %>% 
  dplyr::mutate_at(c("array_preds", "TCGA_preds"), make.names)

# Concordant and Discordant samples
conc <- d %>% dplyr::filter(array_preds == TCGA_preds)
disc <- d %>% dplyr::filter(array_preds != TCGA_preds)

# make sure there are no os_yrs > 100 years
stopifnot(sum(d[["os_yrs"]] > 100, na.rm = TRUE) == 0)
```

## C.3.1 Correlation with Clinical and Pathological Parameters

### BRCA1/2 Mutations

```{r subtype_by_brca}
sb_tab <- d %>% 
  dplyr::filter(!grepl("ARL", ottaID)) %>% 
  dplyr::transmute(
    final = factor(final),
    BRCA1_2
  ) %>% 
  Amisc::describeBy("final", by1 = "BRCA1_2") %>% 
  dplyr::select(-c(Variable, Total, PValue)) %>% 
  dplyr::slice(-1)
pandoc.table(sb_tab, split.tables = Inf)
```

### _Table SC7:_ Cohort characteristics for all cases by subtype

```{r cohort_characteristics_all}
var_names <- c("age_dx", "stage", "residual_disease", "necrosis",
               "BRCA1_2", "race_v1", "anatomical_site")
var_desc <- c("Age at Diagnosis", "Stage", "Residual Disease", "Necrosis",
              "BRCA 1/2", "Race", "Anatomical Site")
d_cohort_all <- d %>%
  dplyr::transmute(final = factor(final), !!!rlang::syms(var_names))
uni_ass_all <- d_cohort_all %>% 
  Amisc::describeBy(var_names, var_desc, "final", p.digits = 2) %>% 
  dplyr::mutate(PValue = ifelse(PValue %in% c("0", "0.00"), "< 0.001", PValue))
pandoc.table(uni_ass_all, split.tables = Inf,
             caption = "Cohort characteristics for all cases by subtype")
```

### _Table SC8:_ Cohort characteristics for all known adnexal sites by subtype

```{r cohort_characteristics_adnexal}
d_cohort_adnexal <- d_cohort_all %>% 
  dplyr::filter(anatomical_site == "adnexal")
var_names_adnexal <- var_names %>% purrr::discard(~ . == "anatomical_site")
var_desc_adnexal <- var_desc %>% purrr::discard(~ . == "Anatomical Site")
uni_ass_adnexal <- d_cohort_adnexal %>% 
  Amisc::describeBy(var_names_adnexal, var_desc_adnexal, "final", p.digits = 2) %>% 
  dplyr::mutate(PValue = ifelse(PValue %in% c("0", "0.00"), "< 0.001", PValue))
pandoc.table(uni_ass_adnexal, split.tables = Inf,
             caption = "Cohort characteristics for all known ovarian site by subtype")
```

### _Table SC9:_ Median Follow-up Time in Years and Events by Final Subtype

```{r follow_up}
# Calculate follow-up times summarized with the median
fu_times <- function(data, time, status, event, group = NULL, digits = 1) {
  if (!is.null(group)) {
    data <- dplyr::group_by(data, .data[[group]])
  }
  fu_dat <- data %>% 
    dplyr::summarize(
      `Observation Time` = median(.data[[time]], na.rm = TRUE),
      `Censoring Time` = median(.data[[time]][.data[[status]] == event], na.rm = TRUE),
      `Reverse KM` = survfit(Surv(.data[[time]], ifelse(.data[[status]] == event, 0, 1)) ~ 1) %>% 
        broom::glance() %>% 
        purrr::pluck("median"),
      Events = sum(.data[[status]] == event, na.rm = TRUE)
    ) %>% 
    dplyr::mutate_if(is.numeric, round, digits = digits)
  if (!is.null(group)) {
    dplyr::rename(fu_dat, Class = group)
  } else {
    tibble::add_column(fu_dat, Class = "Full Cohort", .before = 1)
  }
}
```

```{r times_total}
os_args <- list(time = "os_yrs", status = "os_sts", event = "os.event")
pfs_args <- list(time = "pfs_yrs", status = "pfs_sts", event = "pfs.event")

os_full <- purrr::invoke(fu_times, os_args, data = d)
pfs_full <- purrr::invoke(fu_times, pfs_args, data = d)

os_conc <- purrr::invoke(fu_times, os_args, data = conc)
pfs_conc <- purrr::invoke(fu_times, pfs_args, data = conc)
```

```{r times_final_os}
times_final_os <- os_full %>% 
  rbind(purrr::invoke(fu_times, os_args, data = d, group = "final"))
pandoc.table(
  times_final_os,
  caption = "OS Median Follow-up Time in Years by Final Predictions"
)
```

\  

```{r times_final_pfs}
times_final_pfs <- pfs_full %>% 
  rbind(purrr::invoke(fu_times, pfs_args, data = d, group = "final"))
pandoc.table(
  times_final_pfs,
  caption = "PFS Median Follow-up Time in Years by Final Predictions"
)
```

## C.3.3 Survival Analysis

```{r surv_params_C03}
# Common km arguments (Display legend only for top (OS) survival plot)
km_args <- list(title = c("Overall Survival", "Progression-Free Survival"),
                legend = c(list(c(0.9, 0.9)), "none"))

# Common survival plot arguments
surv_args <- list(
  data = d,
  conf.int = TRUE,
  pval = TRUE,
  pval.method = TRUE,
  risk.table = TRUE,
  risk.table.height = 1/3,
  xlab = "Time in Years",
  ylab = "Survival Probability",
  legend.title = "Class",
  legend.labs = c("C1.MES", "C2.IMM", "C4.DIF", "C5.PRO")
)

# Common combine plot arguments
comb_args <- list(print = TRUE, ncol = 1, nrow = 2)
```

```{r km_final_all, fig.width=7, fig.height=10}
km_final_all <- purrr::list_merge(
  km_args,
    fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ final, data = d),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ final, data = d)
  )
)
plots_km_final_all <- km_final_all %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "All OTTA (Final Model)")
ggsave(file.path(fig_path, "km_final_all.pdf"), plots_km_final_all, width = 7, height = 10)
```

```{r km_final_adnexal, fig.width=7, fig.height=10}
# Filter for adnexal sites
d_adnexal <- dplyr::filter(d, anatomical_site %in% c("adnexal", "presumed adnexal"))
surv_args_adnexal <- purrr::map_at(surv_args, "data", ~ d_adnexal)

km_final_adnexal <- purrr::list_merge(
  km_args,
    fit = list(
    survfit(Surv(os_yrs10, os_sts10 == "os.event") ~ final, data = d_adnexal),
    survfit(Surv(pfs_yrs10, pfs_sts10 == "pfs.event") ~ final, data = d_adnexal)
  )
)
plots_km_final_adnexal <- km_final_adnexal %>% 
  purrr::pmap(~ purrr::invoke(ggsurvplot, surv_args_adnexal, title = ..1, legend = ..2, fit = ..3)) %>% 
  purrr::invoke(arrange_ggsurvplots, comb_args, x = ., title = "All Adnexal Sites OTTA (Final Model)")
ggsave(file.path(fig_path, "km_final_adnexal.pdf"), plots_km_final_adnexal, width = 7, height = 10)
```

```{r mvs_dat}
mvs_dat <- d %>% 
  dplyr::transmute(
    final = factor(final),
    residual_disease,
    BRCA1_2,
    age_dx,
    stage,
    anatomical_site,
    cd8,
    os_yrs,
    os_sts,
    pfs_yrs,
    pfs_sts
  ) %>% 
  as.data.frame()

mvs_args <- list(
  input.d = mvs_dat,
  stat.test = "logtest",
  var.names.surv.time = c("os_yrs", "pfs_yrs"),
  var.names.surv.status = c("os_sts", "pfs_sts"),
  event.codes.surv = c("os.event", "pfs.event"),
  surv.descriptions = c("OS", "PFS"),
  show.var.detail = TRUE,
  show.group.name.for.bin.var = TRUE,
  round.small = TRUE
)
```

### _Table SC10:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, residual disease, BRCA mutation, age, stage, and CD8

```{r mvs_all}
var_all <- purrr::set_names(
  c("final", "residual_disease", "BRCA1_2", "age_dx", "stage", "cd8"),
  c("Final Subtype", "Residual Disease", "BRCA 1/2 mutation", "Age", "Stage", "CD8")
)
mvs_all <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_all %>%
    purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses: all covariates"
)
cat(mvs_all[["result.table.bamboo"]])
```

### _Table SC11:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, residual disease, age, stage, and CD8

```{r mvs_all_no_brca1_2}
var_all_no_brca1_2 <- purrr::discard(var_all, ~ . == "BRCA1_2")
mvs_all_no_brca1_2 <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_all_no_brca1_2 %>%
    purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses: all covariates except BRCA 1/2"
)
cat(mvs_all_no_brca1_2[["result.table.bamboo"]])
```

### _Table SC12:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, BRCA mutation, age, stage, and CD8

```{r mvs_all_no_resdx}
var_all_no_resdx <- purrr::discard(var_all, ~ . == "residual_disease")
mvs_all_no_resdx <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_all_no_resdx %>% 
    purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses: all covariates except residual disease"
)
cat(mvs_all_no_resdx[["result.table.bamboo"]])
```

### _Table SC13:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, BRCA mutation, age and stage

```{r mvs_all_no_cd8}
var_all_no_cd8 <- purrr::discard(var_all, ~ . == "cd8")
mvs_all_no_cd8 <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_all_no_cd8 %>% 
    purrr::splice(
      mvs_args,
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses: all covariates except CD8"
)
cat(mvs_all_no_cd8[["result.table.bamboo"]])
```

### _Table SC14:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, residual disease, BRCA mutation, age, stage, and CD8 (adnexal sites only)

```{r mvs_adnexal}
mvs_adnexal <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_all %>%
    purrr::splice(
      mvs_args %>%
        purrr::map_at("input.d", dplyr::filter, anatomical_site == "adnexal"),
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses on Adnexal Sites Only: all covariates"
)
cat(mvs_adnexal[["result.table.bamboo"]])
```

### _Table SC15:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, residual disease, age, stage, and CD8 (adnexal sites only)

```{r mvs_adnexal_no_brca_12}
var_adnexal_no_brca_12 <- purrr::discard(var_all, ~ . == "BRCA1_2")
mvs_adnexal_no_brca_12 <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_adnexal_no_brca_12 %>%
    purrr::splice(
      mvs_args %>%
        purrr::map_at("input.d", dplyr::filter, anatomical_site == "adnexal"),
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses on Adnexal Sites Only: all covariates except BRCA 1/2"
)
cat(mvs_adnexal_no_brca_12[["result.table.bamboo"]])
```

### _Table SC16:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, BRCA mutation, age, stage, and CD8 (adnexal sites only)

```{r mvs_adnexal_no_resdx}
var_adnexal_no_resdx <- purrr::discard(var_all, ~ . == "residual_disease")
mvs_adnexal_no_resdx <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_adnexal_no_resdx %>%
    purrr::splice(
      mvs_args %>%
        purrr::map_at("input.d", dplyr::filter, anatomical_site == "adnexal"),
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses on Adnexal Sites Only: all covariates except residual disease"
)
cat(mvs_adnexal_no_resdx[["result.table.bamboo"]])
```

### _Table SC17:_ Multivariable survival analysis of overall and progression-free survival, adjusting for final subtype, BRCA mutation, age and stage (adnexal sites only)

```{r mvs_adnexal_no_cd8}
var_adnexal_no_cd8 <- purrr::discard(var_all, ~ . == "cd8")
mvs_adnexal_no_cd8 <- purrr::invoke(
  .f = doCoxphMultivariable,
  .x = var_adnexal_no_cd8 %>%
    purrr::splice(
      mvs_args %>%
        purrr::map_at("input.d", dplyr::filter, anatomical_site == "adnexal"),
      var.names = .,
      var.descriptions = names(.),
      var.ref.groups = purrr::rep_along(., NA)
    ),
  caption = "Multivariable Analyses on Adnexal Sites Only: all covariates except CD8"
)
cat(mvs_adnexal_no_cd8[["result.table.bamboo"]])
```
