---
output:
  word_document:
    reference_docx: styles.docx
    fig_height: 5
    fig_width: 7
params:
  outputDir: outputDir
---

# B.6 Pre-processing, Batch Effect, QC and Normalization of the NanoString Data

```{r setup_B06, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "asis"
)
```

```{r load_B06}
# Load packages, helpers, input data
library(ggplot2)
library(here)
source(here("pipeline/7-supplementary/utils.R"))

arl_dat <-
  readxl::read_excel(here("data/nstring/Nanostring_ARL-all samples-all gnes_20180607.xlsx"))
load(here("data/supp/expCS.rda"))
load(here("data/supp/exp_CS3_all.rda"))
load(here("data/supp/cs3.norm.rda"))

fig_path <- file.path(params$outputDir, "supplementary/figures/B06")
```

## QC Table

- **Sample Quality** fails if either **Limit of Detection** or **Signal to Noise** fail
- **Overall QC** fails if either **Smallest Positive Control**, **Imaging**, or **Linearity** fail

```{r qc_filter}
# Filter QC samples
exp_CS3_final <- exp_CS3_all %>%
  dplyr::mutate(
    ottaID = magrittr::inset(
      ottaID,
      match("X20151128_OTTA047AOCSH_TAOC10308_08", File.Name),
      "TAOC10303"
    ),
    lodFlag = factor(ifelse(pergd < 50, "Failed", "Passed")),
    snFlag = factor(ifelse(sn < 170, "Failed", "Passed"))
  ) %>%
  dplyr::anti_join(arl_dat, by = "File.Name")
```

```{r qc_table}
# QC Table flag counts
counts <- exp_CS3_final %>%
  dplyr::group_by(nanostring.site) %>%
  dplyr::summarize(
    `Imaging Failures` = sum(imagingFlag == "Failed"),
    `Linearity Failures` = sum(linFlag == "Failed"),
    `Smallest PC Failures` = sum(spcFlag == "Failed"),
    `Limit of Detection Failures` = sum(lodFlag == "Failed"),
    `Signal to Noise Failures` = sum(snFlag == "Failed"),
    `Sample Quality Failures` = sum(normFlag == "Failed"),
    `Overall QC Failures` = sum(QCFlag == "Failed")
  ) %>% 
  as.data.frame() %>% 
  tibble::column_to_rownames("nanostring.site") %>% 
  cbind(`Total Samples Run` = as.numeric(table(exp_CS3_final[["nanostring.site"]])), .) %>% 
  rbind(Total = colSums(.), .) %>% 
  t()

# QC Table flag percentages
pcts <- rbind(
  `Total Samples Run` = round(counts[1, ] / counts[1, 1], 3) * 100,
  round(counts[-1, ] %*% diag(1 / counts[1, ]), 3) * 100
) %>% 
  apply(1:2, function(x) paste0("(", format(x, nsmall = 1), "%)"))

# Combined counts and pcts. Custom bolding and line break
counts[] <- matrix(paste(counts, pcts))
rownames(counts)[c(1, 7, 8)] <- paste0("**", rownames(counts)[c(1, 7, 8)], "**")
counts <- rbind(counts[1:6, ], "<br>", counts[7:8, ])

pander::pandoc.table(
  counts,
  justify = "lrrrr",
  emphasize.rownames = FALSE,
  split.tables = Inf
)
```

## Signal/Noise vs % Genes Detected

```{r snr_vs_pergd}
# SNR vs %GD
p <- ggplot(exp_CS3_all, aes(sn, pergd, color = nanostring.site)) +
  geom_point() +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_vline(xintercept = 170, color = "brown", size = 1) +
  lims(x = c(0, 5000)) +
  labs(x = "Signal/Noise Ratio",
       y = "Percent of Genes Detected",
       title = "Signal/Noise vs % Genes Detected") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_color_discrete(name = "Site",
                       labels = c("Melbourne", "San Francisco", "Vancouver"))

print(p)
ggsave(file.path(fig_path, "snr_vs_pergd.pdf"), p, width = 7, height = 5)
```

## Reference Pools Over Time

```{r pools_data}
# Pools data
pools <- expCS %>% 
  dplyr::filter(sample.type %in% c("XSITE.ORIG", "XSITE.FOR", "POOL"),
                geneRLF == "CS3") %>% 
  dplyr::mutate(ref.type = factor(dplyr::case_when(
    POOL1 == "Yes" ~ "POOL 1",
    POOL2 == "Yes" ~ "POOL 2",
    POOL3 == "Yes" ~ "POOL 3",
    cross.site.control == "Yes" ~ "Cross Site",
    TRUE ~ NA_character_
  ))) %>% 
  dplyr::filter(ref.type != "Cross Site") %>% 
  dplyr::mutate(
    nanostring.date = as.Date(nanostring.date),
    averageHK = log2(averageHK),
    nanostring.site = dplyr::case_when(
      nanostring.site == "AOC" ~ "Melbourne",
      nanostring.site == "USC" ~ "San Francisco",
      TRUE ~ "Vancouver"
    )
  )
```

```{r pools_gx_time}
# Reference pools gx across site and time
p <- ggplot(pools, aes(nanostring.date, averageHK, colour = nanostring.site)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_grid(vars(ref.type), vars(nanostring.site)) +
  labs(x = "Time",
       y = "Average Expression (log2)",
       title = "CodeSet3 Reference Pool Expression across Site and Time") +
  lims(y = c(13, 19)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_x_date(date_breaks = "3 months", date_labels =  "%b %Y") +
  scale_color_discrete(name = "Site",
                       labels = c("Melbourne", "San Francisco", "Vancouver"))

print(p)
ggsave(file.path(fig_path, "pools_gx_time.pdf"), p, width = 7, height = 5)
```

## Data Consistency of Cross-Site Controls Across Sites

```{r cross-site}
# Cross site
cross.site <- expCS %>% 
  dplyr::filter(sample.type %in%
                  c("Cross site", "XSITE.ORIG", "XSITE.FOR", "POOL")) %>% 
  dplyr::mutate(ref.type = factor(dplyr::case_when(
    POOL1 == "Yes" ~ "POOL 1",
    POOL2 == "Yes" ~ "POOL 2",
    POOL3 == "Yes" ~ "POOL 3",
    cross.site.control == "Yes" ~ "Cross Site",
    TRUE ~ NA_character_
  ))) %>% 
  dplyr::filter(geneRLF == "CS3",
                ref.type == "Cross Site",
                summaryID != "TVAN20681") %>% 
  dplyr::mutate(nanostring.site = factor(dplyr::case_when(
    nanostring.site == "AOC" ~ "Melbourne",
    nanostring.site == "USC" ~ "San Francisco",
    TRUE ~ "Vancouver"
  )))
```

```{r cross-site-each-site}
# Cross-site for each site
VanRefs.gx <- cross.site %>% 
  dplyr::filter(nanostring.site == "Vancouver") %>% 
  dplyr::arrange(summaryID) %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)

AOCRefs.gx <- cross.site %>% 
  dplyr::filter(nanostring.site == "Melbourne") %>% 
  dplyr::arrange(summaryID) %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)

USCRefs.gx <- cross.site %>% 
  dplyr::filter(nanostring.site == "San Francisco") %>% 
  dplyr::arrange(summaryID) %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)
```

```{r pools-each-site}
# Pools for each site
vanpools <- pools %>% 
  dplyr::filter(nanostring.site == "Vancouver") %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)

AOCpools <- pools %>% 
  dplyr::filter(nanostring.site == "Melbourne") %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)

USCpools <- pools %>% 
  dplyr::filter(nanostring.site == "San Francisco") %>% 
  dplyr::pull(File.Name) %>% 
  dplyr::select(cs3.norm, .)
```

```{r norm}
# Everything is calibrated to Vancouver
AOCRefs.gx2 <- 
  t(nanostringr::refMethod(t(AOCRefs.gx), t(vanpools), t(AOCpools)))
USCRefs.gx2 <-
  t(nanostringr::refMethod(t(USCRefs.gx), t(vanpools), t(USCpools)))
```

```{r cc_combine}
# Combinations of cross-site gene expression
sites <- c("USC", "AOC", "VAN")
all_xsites <- combn(sites, 2) %>% 
  tibble::as_tibble() %>% 
  purrr::set_names(purrr::map_chr(., paste, collapse = "_vs_"))

# Combined gene expression
all_gx <- list(USCRefs.gx2, AOCRefs.gx2, VanRefs.gx) %>% 
  purrr::set_names(sites) %>% 
  purrr::map(~ as.data.frame(t(.)))

# Concordance measures for all genes averaged across samples
all_metrics <- all_xsites %>% 
  purrr::imap_dfr(~ {
    purrr::pmap_dfr(all_gx[.x], ~ {
      R2 <- cor(.x, .y) ^ 2
      ccc <- epiR::epi.ccc(.x, .y)
      Ca <- purrr::pluck(ccc, "C.b")
      Rc <- purrr::pluck(ccc, "rho.c", "est")
      tibble::lst(R2, Ca, Rc)
    }) %>% 
      dplyr::mutate(Sites = .y)
  }) %>% 
  tidyr::gather(key = "Metric", value = "Expression", -Sites)
```

```{r cc_hist}
# Plot all combinations of cross-site concordance measure histograms
p <- ggplot(all_metrics, aes(Expression)) +
  geom_histogram(bins = 30, fill = "blue") +
  facet_grid(rows = vars(Sites), cols = vars(Metric), scales = "free_x") +
  labs(y = "Count",
       title = "Cross-Site Concordance Measure Distributions") +
  theme_bw() +
  theme(panel.grid.minor = element_blank())

print(p)
ggsave(file.path(fig_path, "cc_hist.pdf"), p, width = 7, height = 5)
```

Concordance Measures:

- Ca: coefficient of accuracy
- R2: squared Pearson's correlation coefficient
- Rc: Lin's concordance correlation

```{r avg_scatter, fig.height=10, results='hide'}
# Combined averaged gene expression
all_gx_avg <- purrr::map_dfr(all_gx, rowMeans)
par(mfrow = c(3, 1))
purrr::walk(all_xsites, ~ {
  nanostringr::CCplot(
    method1 = all_gx_avg[[.[1]]],
    method2 = all_gx_avg[[.[2]]],
    xlabel = .[1],
    ylabel = .[2],
    title = paste("Average Concordance Correlation for", .[1], "vs", .[2]),
    Ptype = "scatter"
  )
})
dev.print(
  pdf,
  file.path(fig_path, "avg_scatter.pdf"),
  width = 7,
  height = 10
)
```
